Examples of Customization

### 2017-05-16 writing/EpiDraft.Rmd

```{r, echo=FALSE}
#I used the variable "Legionellosis, Current week" so hopefully that's right
leg1 <- read.csv("../Legionnaires data/2014Leg.csv")[,c(2,3,24)]
leg2 <- read.csv("../Legionnaires data/2015Leg.csv")[,c(2,3,24)]
leg3 <- read.csv("../Legionnaires data/2016Leg.csv")[,c(2,3,24)]
leg <- data.frame(year = c(leg1$MMWR.Year, leg2$MMWR.Year, leg3$MMWR.Year), week = c(leg1$MMWR.Week, leg2$MMWR.Week, leg3$MMWR.Week), cases = c(leg1$Legionellosis..Current.week, leg2$Legionellosis..Current.week, leg3$Legionellosis..Current.week))
plot(leg$cases, xlab = "Week", ylab = "Number of Cases", main = "Legionnaire's Disease 2014-2016")
```

@@

#Row 48 is the only row with different states. 569 and 574 have NA in every column.
```

```{r}
library(lubridate)
library(dplyr)
#Precipitation data for New York City and Philadelphia:
parain <- readRDS("data/pa.rds")
nyrain <- readRDS("data/pa.rds")
paquant <- quantile(parain$prcp, probs = c(.75, .95, .99), na.rm=T)
nyquant <- quantile(nyrain$prcp, probs = c(.75, .95, .99), na.rm=T)
parain$quant75 <- ifelse(parain$prcp>paquant[1], 1,0)
parain$quant95 <- ifelse(parain$prcp>paquant[2], 1,0)
parain$quant99 <- ifelse(parain$prcp>paquant[3], 1,0)
nyrain$quant75 <- ifelse(nyrain$prcp>nyquant[1], 1,0)
nyrain$quant95 <- ifelse(nyrain$prcp>nyquant[2], 1,0)
nyrain$quant99 <- ifelse(nyrain$prcp>nyquant[3], 1,0)
parain$month <- month(parain$date)
parain$year <- year(parain$date)
nyrain$month <- month(nyrain$date)
nyrain$year <- year(nyrain$date)
#Monthly rainfall above 75th, 95th, and 99th percentiles for Philly and NYC
pamonthly <- group_by(parain, month, year) %>% summarise(quant75 =mean(quant75), quant95=mean(quant95), quant99=mean(quant99))
nymonthly <- group_by(nyrain, month, year) %>% summarise(mean(quant75), mean(quant95), mean(quant99))
#What pattern is this?
ggplot(pamonthly, aes(x=1:136, y=quant95))+geom_line()+geom_vline(xintercept=seq(from=1, to=136, by=12), col="red") + ggtitle("Monthly rainfall for Philadelphia 2006-2017")+ ylab("Proportion of days over 95th percentile")
```

```{r}
#Power analysis using eesim

@@

We can pull the trend from this data:

```{r}
```

### Simulated Data with Similar Trend

Many epidemiologic data sets are of a sensitive nature and not publicly available.  We can use eesim to simulate data with a similar seasonal trend to fit and assess models.

```{r, echo=F}
#Means of real data:
map(leg_cases[,2:4], mean, na.rm=T)
#(ma=14.633, nyc=4.69, pa=5.314)
exposure <- continuous_exposure(n=1001, mu = 65, sd = 5, trend = "cos1", amp=.4)
#Make this into weekly data instead of daily.
x <- seq.int(from=1, to=1001, by=7)
weeklyexp <- exposure[x,]
plot(weeklyexp, main = "Plot of Exposure values")
outcome <- sim_outcome(weeklyexp, average_outcome = 4.69, trend = "no trend")
plot(outcome$outcome)

>>>>

@@

#Row 48 is the only row with different states. 569 and 574 have NA in every column.

@@

```{r}
library(lubridate)
library(dplyr)
#Precipitation data for New York City and Philadelphia:
parain <- readRDS("data/pa.rds")
nyrain <- readRDS("data/ny.rds")
paquant <- quantile(parain$prcp, probs = c(.75, .95, .99), na.rm=T)
nyquant <- quantile(nyrain$prcp, probs = c(.75, .95, .99), na.rm=T)
parain$quant75 <- ifelse(parain$prcp>paquant[1], 1,0)
parain$quant95 <- ifelse(parain$prcp>paquant[2], 1,0)
parain$quant99 <- ifelse(parain$prcp>paquant[3], 1,0)
nyrain$quant75 <- ifelse(nyrain$prcp>nyquant[1], 1,0)
nyrain$quant95 <- ifelse(nyrain$prcp>nyquant[2], 1,0)
nyrain$quant99 <- ifelse(nyrain$prcp>nyquant[3], 1,0)
parain$month <- month(parain$date)
parain$year <- year(parain$date)
nyrain$month <- month(nyrain$date)
nyrain$year <- year(nyrain$date)
#Monthly rainfall above 75th, 95th, and 99th percentiles for Philly and NYC
pamonthly <- group_by(parain, year, month) %>% summarise(quant75 =mean(quant75), quant95=mean(quant95), quant99=mean(quant99))
nymonthly <- group_by(nyrain, year, month) %>% summarise(mean(quant75), quant95 = mean(quant95), mean(quant99))
#What pattern is this?
ggplot(pamonthly, aes(x=1:136, y=quant95))+geom_line()+geom_vline(xintercept=seq(from=1, to=136, by=12), col="red") + ggtitle("Monthly rainfall for Philadelphia 2006-2017")+ ylab("Proportion of days over 95th percentile")

#Check if proportion constant averaging over months:
plot(pamonthly %>% group_by(month) %>% summarise(mean1 = mean(quant95, na.rm=T)))
plot(nymonthly %>% group_by(month) %>% summarise(mean1 = mean(quant95, na.rm=T)))
#These two plots display a similar pattern, so we will use the monthly probabilities for PA in our simulation.
rainprobs <-pamonthly %>% group_by(month) %>% summarise(mean1 = mean(quant95, na.rm=T))
```

### Simulated Data with Monthly Exposure Trend

Many epidemiologic data sets are of a sensitive nature and not publicly available.  We can use eesim to simulate data with a similar seasonal trend to fit and assess models.  Because rainfall in Pennsylvania and New York exhibited similar montly patterns, we will use the average proportion of days each month from 2006-2017 which had rainfall in the 95th percentile.  We will specify these proportions in the "monthly" exposure trend.

```{r, echo=F}
#Means of real data:
map(leg_cases[,2:4], mean, na.rm=T)
#(ma=14.633, nyc=4.69, pa=5.314)
simdat <- eesim(n=3650, n_reps=1, rr=1.1, exposure_type = "binary", central = c(0.048, 0.035, 0.046, 0.036, 0.035, 0.055, 0.053, 0.067, 0.070, 0.053, 0.033, 0.067), exposure_trend = "monthly", average_outcome = 5.314453)
```

### 2017-05-16 writing/custom_examples.Rmd

```{r}
sintrend <- function(n, y){
  day <- c(1:n)
  1 + y * sin(2 * pi * (day / 365))
}
binsin <- function(n, y, p){
  day <- c(1:n)
  seasont <- p + y * sin(2 * pi * (day / 365))
}
calc_t(n = 5, y = .3, custom_func = sintrend)
plot(calc_t(1000, y = 2, custom_func = sintrend))
plot(bin_t(1000, p=.3, trend="cos1"))
plot(bin_t(1000, p=.3, custom_func=binsin, y=.1))
```

@@

##Custom function for model

```{r}
trivial_mod <- function(df, constant){
  newx <- constant*df$x
  mod <- lm(outcome~newx, data=df)
  out_1 <- summary(mod)$coef[2, ]
  out_2 <- stats::confint.default(mod)[2, ]
  out <- c(out_1, out_2)
  return(out)
}
```

>>>>

```{r}
sintrend <- function(n, y){
  day <- c(1:n)
  1 + y * sin(2 * pi * (day / 365))
}
binsin <- function(n, y, p){
  day <- c(1:n)
  p + y * sin(2 * pi * (day / 365))
}
calc_t(n = 5, y = .3, custom_func = sintrend)
plot(calc_t(1000, y = 2, custom_func = sintrend))
plot(bin_t(1000, p=.3, trend="cos1"))
plot(bin_t(n= 1000, p=.3, custom_func=binsin, y=.1))
```

@@
